\documentclass{beamer}

\usetheme{Boadilla}
\usecolortheme{default}

\title{AR-Based NET Application for RBTs}
\author{Alexis Bryan Ambriz}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Introduction}
  \begin{itemize}
    \item Problem statement: The challenges faced by Registered Behavioral Technicians (RBTs) in accurately and efficiently collecting data during ABA therapy sessions.
    \item Solution: An AR-based NET application that streamlines data collection, enhances therapy effectiveness, and minimizes disruptions to the child's experience.
    \item Value proposition: A less intrusive, more accurate, and time-saving tool for RBTs.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Team}
  \begin{itemize}
    \item Highlight the team's expertise in AR development, ABA, and UX design.
    \item Showcase relevant experience and qualifications.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Technology}
  \begin{itemize}
    \item Explain the Unity Experiment Framework and its role in streamlining data collection and analysis.
    \item Discuss other key technologies (e.g., AI, AR hardware) that can enhance the user experience.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Market Analysis}
  \begin{itemize}
    \item Present the target market size and demographics of RBTs and ABA therapy providers.
    \item Identify potential competitors and their strengths/weaknesses.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Product}
  \begin{itemize}
    \item Demonstrate the application's features, such as real-time data collection, automated scoring, and customizable prompts.
    \item Highlight how the AR interface minimizes distractions for the child.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Business Model}
  \begin{itemize}
    \item Outline the revenue streams (e.g., subscription-based, licensing).
    \item Discuss the cost structure and profitability.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Marketing and Sales Strategy}
  \begin{itemize}
    \item Describe the marketing channels and tactics to reach RBTs and ABA therapy providers.
    \item Explain the sales approach and potential partnerships.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Financial Projections}
  \begin{itemize}
    \item Present the projected revenue, expenses, and profitability.
    \item Discuss the funding requirements.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Team and Advisors}
  \begin{itemize}
    \item Introduce the core team and any key advisors.
    \item Highlight their expertise and commitment.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Call to Action}
  \begin{itemize}
    \item Clearly state the desired outcome (e.g., investment, partnership).
    \item Encourage the audience to support the development of this innovative tool for RBTs.
  \end{itemize}
\end{frame}

\end{document}